An Implementation of the Active Contours without Edged model and the Logic Framework for Active contours on multi-channel images

### 2010-12-12 trunk/cs870/project/Report/Paper.tex
updates style

\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran}
\usepackage{cite}
\usepackage{url}
\usepackage{times}
\usepackage{graphicx}
\usepackage{url}
\usepackage{clrscode}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{color}
\usepackage{balance}

@@

% The paper headers
\markboth{CS870 Project Report - Active Contour without Edges}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
}

@@

@@

\begin{table*}[h!t!]
\centering
\begin{tabular}{ c | c |c}
\textbf{Criteria} & \textbf{Goal} & \textbf{Applies to Model}\\
\hline\hline
Detecting Boundaries & Ability to correctly detect object boundaries of simple objects& Both Models\\
\hline
Curve Position & Ability to correctly detect object boundaries irrespective of the initial curve position & Both Models\\
\hline
Detecting Holes & Ability to detect holes in objects, and not simply stop on outside boundary & Both Models\\
\hline
Blurred Images & Ability to correctly (as much as possible) detect object boundaries in blurred images & Both Models\\
\hline
Noisy Images & Ability to correctly (as much as possible) detect object boundaries in noisy images & Both Models\\
\hline
Union Operator & Ability to correctly obtain the union of two or more images & Sandberg-Chan\\
\hline
Intersection Operator & Ability to correctly obtain the intersection of two or more images & Sandberg-Chan\\
\hline
Complement & Ability to correctly obtain the union or intersection of two or more images containing complements & Sandberg-Chan\\
\hline
Parameter Settings & Ability to respond correctly to the different parameter settings & Both Models\\
\end{tabular}
\centering
\caption{Evaluation Criteria}
\label{tab:criteria}
\end{table*}

@@

There are mainly three parameters in this model that can be varied: $\mu, \lambda_{1}, \lambda_{2}$. We would usually want both $\lambda_{1}$ and $\lambda_{2}$
to be equal to 1 to indicate that we care both about the difference of intensities inside and outside. A smaller weighting for one of them would mean that we
would ignore some of the variances in intensities in this area. A larger weighting means that we are magnifying the difference in intensities in that area
(i.e. we want to detect any minor changes). We show an example of these variations in Figure~\ref{fig:cv_eg12} where we keep $\lambda_{2}$ constant, and vary
$lambda_1$. When we set $\lambda_1 = 0.2$, it is shown that less details within the interior of the brain is detected. When we set $\lambda_2 = 2$, we can see
that more details within the brain are detected.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg12.png}
\caption{Effect of varying $\lambda_1$ which controls how much details are detected inside the contour.}
\label{fig:cv_eg12}
\end{figure*}

$\lambda_1 = \lambda_2 = 1$
$\lambda_1 = 2, \lambda_2 = 1$
$\lambda_1 = 0.2, \lambda_2 = 1$

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{cite}
\usepackage{url}
\usepackage{graphicx}
\usepackage{clrscode}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{color}
\usepackage{balance}

\cvprfinalcopy
\ifcvprfinal\pagestyle{empty}\fi

@@

@@

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}

@@

\begin{table*}[h!t!]
\centering
\resizebox{\textwidth }{!}{
\begin{tabular}{ c | c |c}
\textbf{Criteria} & \textbf{Goal} & \textbf{Applies to Model}\\
\hline\hline
Detecting Boundaries & Ability to correctly detect object boundaries of simple objects& Both Models\\
\hline
Curve Position & Ability to correctly detect object boundaries irrespective of the initial curve position & Both Models\\
\hline
Detecting Holes & Ability to detect holes in objects, and not simply stop on outside boundary & Both Models\\
\hline
Blurred Images & Ability to correctly (as much as possible) detect object boundaries in blurred images & Both Models\\
\hline
Noisy Images & Ability to correctly (as much as possible) detect object boundaries in noisy images & Both Models\\
\hline
Union Operator & Ability to correctly obtain the union of two or more images & Sandberg-Chan\\
\hline
Intersection Operator & Ability to correctly obtain the intersection of two or more images & Sandberg-Chan\\
\hline
Complement & Ability to correctly obtain the union or intersection of two or more images containing complements & Sandberg-Chan\\
\hline
Parameter Settings & Ability to respond correctly to the different parameter settings & Both Models\\
\end{tabular}
}
\centering
\caption{Evaluation Criteria}
\label{tab:criteria}
\end{table*}

@@

There are mainly three parameters in this model that can be varied: $\mu, \lambda_{1}, \lambda_{2}$. We would usually want both $\lambda_{1}$ and $\lambda_{2}$
to be equal to 1 to indicate that we care both about the difference of intensities inside and outside. A smaller weighting for one of them would mean that we
would ignore some of the variances in intensities in this area. A larger weighting means that we are magnifying the difference in intensities in that area
(i.e. we want to detect any minor changes). We show an example of these variations in Figure~\ref{fig:cv_eg12} where we vary
$lambda_1$ and $\lambda_2$. When we set $\lambda_1 = 0.2$ and $\lambda_2 = 1$, less details within the interior of the brain is detected. When
we set $\lambda_1 = 2$ and $\lambda_2 = 1$, we can see that more details within the brain are detected. When we set $\lambda_1 = 5$, and $\lambda_2 = 0.01$ (a
very extreme case), we can see that parts of outside boundaries are not well detected, while many details are detected within the brain.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg12.png}
\caption{Effect of varying $\lambda_1$ which controls how much details are detected inside the contour. The figure shows the segmentation in each case.}
\label{fig:cv_eg12}
\end{figure*}

The second parameter, $\mu$ controls how much we allow the length of the curve to increase. If $\mu$ is small, it means that the curve length can increase to
detect multiple smaller objects without penalizing our minimization problem. On the other hand if $\mu$ is large, it means that any change in the curve length
will be scaled up, and thus will limit the curve expansion to keep the force to a minimum. Unfortunately, we were not able to see this effect in our
experiments. We tried varying increasing $\mu$ to be able to detect groupings of objects instead of the individual objects, but the segmentation was invariant
to $\mu$. We give more details about how we tried to handle this, and why we believe it is not working in Section~\ref{sec:difficulties}.
